This document describes a software tool for object tracking in video data, developed for road traffic monitoring and safety diagnosis. It is part of a larger collection of software tools for transportation called Traffic Intelligence.

The tool relies on feature-\/based tracking, a robust object tracking methods, particularly suited for the extraction of traffic data such as trajectories and speeds. The best description of this method is given in \href{http://nicolas.saunier.confins.net/data/saunier06crv.html}{\tt this paper}. The program has a command line interface and this document will shortly explain how to use the tool. Keep in mind this is a work in progress and major changes are continuously being made.\hypertarget{feature_based_tracking_License}{}\subsection{License}\label{feature_based_tracking_License}
The code is licensed under the M\-I\-T open source license (\href{http://www.opensource.org/licenses/mit-license}{\tt http\-://www.\-opensource.\-org/licenses/mit-\/license}).

If you make use of this piece of software, please cite one of my paper, e.\-g. N. Saunier, T. Sayed and K. Ismail. Large Scale Automated Analysis of Vehicle Interactions and Collisions. Transportation Research Record\-: Journal of the Transportation Research Board, 2147\-:42-\/50, 2010. I would be very happy in any case to know about any use of the code, and to discuss any opportunity for collaboration.

Contact me at \href{mailto:nicolas.saunier@polymtl.ca}{\tt nicolas.\-saunier@polymtl.\-ca} and learn more about my work at \href{http://nicolas.saunier.confins.net}{\tt http\-://nicolas.\-saunier.\-confins.\-net}. 